\Title

### 2021-06-25 manuscript/content.tex
Review the least-squares part

\noindent where
$\mathbf{W}$ is a $N \times N$ diagonal matrix of data weights and
$\lambda_d$ is a positive \emph{damping} parameter with the same units as the
Jacobian matrix elements.
The second term on the right-hand side of the equation is a zeroth-order
Tikhonov regularization \citep{tikhonov1977} (also known as a damping
regularization or ridge regression) that is used to stabilize the solution.
The damping parameter controls the amount of regularization that will be applied.
An overly large value would generate a smooth solution that fails to reproduce
the high frequency components of the data, while an overly small value would
result in over-fitting, thus failing to produce realistic interpolation results
\citep{martinez2016}.

The range of acceptable values for the damping parameter $\lambda_d$ will
depend on the values of the Jacobian matrix $\mathbf{A}$ and the coefficients.
Consequently, this range will vary (often dramatically) between datasets,
making it difficult to choose an appropriate value for $\lambda_d$ in practice.

@@

\noindent where $\mathbf{B}$ is the scaled and dimensionless Jacobian matrix
and $\mathbf{m}$ is a vector containing scaled coefficients with the same units
as the data.

@@

\noindent where $\lambda$ is a \emph{dimensionless} damping parameter and
regularization is applied on the scaled coefficients $\mathbf{m}$ instead of
$\mathbf{c}$.
Using a dimensionless damping parameter allows us to narrow the range of values
of $\lambda$ that would generate the most accurate predictions, irrespective
of the dataset and its units.
From experience, we recommend searching for suitable $\lambda$ values between
$10^{-6}$ and $10^{4}$ varying by order-of-magnitude.
The choice of the damping and other hyper-parameters like the source depth
could be done through well-established statistical methods, such as
cross-validation.

>>>>

\noindent where
$\mathbf{W}$ is a $N \times N$ diagonal matrix of data weights and
$\lambda_d$ is a positive \emph{damping} parameter with the same units as the
Jacobian matrix elements.
The second term on the right-hand side of Eq.~\ref{eq:misfit-unscaled} is the
zeroth-order Tikhonov regularization \citep{tikhonov1977}, also known as a
damping regularization, that is used to stabilize the solution.

The damping parameter controls the amount of regularization that will be
applied.
An overly large value would generate a smooth solution that fails to reproduce
the high frequency components of the data, while an overly small value would
result in over-fitting, thus failing to produce realistic interpolation results
\citep{martinez2016}.
The range of acceptable values for the damping parameter $\lambda_d$ will
depend on the values of the Jacobian matrix $\mathbf{A}$ and the coefficients.
Consequently, this range will vary (often dramatically) between datasets,
making it difficult to choose an appropriate value in practice.

@@

\noindent where $\mathbf{B} = \mathbf{A} \mathbf{S}\inv$ is the scaled and
dimensionless Jacobian matrix
and $\mathbf{m} = \mathbf{S} \mathbf{c}$ is a vector containing scaled
coefficients with the same units as the data.

@@

\noindent where $\lambda$ is a \emph{dimensionless} damping parameter and
regularization is applied on the scaled coefficients $\mathbf{m}$ instead of
$\mathbf{c}$.
Using a dimensionless damping parameter allows us to narrow the range of values
of $\lambda$ that would generate the most accurate predictions, irrespective
of the dataset and its units.
From experience, we recommend searching for suitable $\lambda$ values between
$10^{-6}$ and $10^{4}$ varying by order-of-magnitude.
The choice of the damping and other hyper-parameters, like the source depth,
could be done through well-established statistical methods, such as
cross-validation.
